\bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in \textit{Drosophila melanogaster}

### 2018-02-24 latex/paper.tex
Updates, fixes from editing

@@

\begin{abstract}
  \vspace*{-0.7em}
  Cilia are sensory organelles that are important for human development
  and physiology.
  A large number of genetic disorders affecting cilia are associated with
  mutations in proteins that localize to the transition zone (TZ),
  a structure at the base of cilia required for ciliogenesis and
  regulation of trafficking in and out of the cilium.
  Here, we report that the membrane lipid phosphatidylinositol
  4,5-bisphosphate(\PIP{}) is essential for proper maturation and function
  of TZs in the male \textit{Drosophila melanogaster} germline.
  Reduction of cellular \PIP{} levels by expression of the
  \textit{Salmonella} phosphoinositide phosphatase SigD or mutation of
  the type I phosphatidylinositol phosphate kinase (PIPKI) Skittles (Sktl)
  induces hyperelongation of TZs following their docking at the plasma
  membrane.
  We provide evidence that these hyperelongated TZs are functionally
  defective, and that the Exo84 mutant \textit{onion rings} decouples
  TZ hyperelongation from the role for \PIP{} in cilium-membrane
  tethering.
  Our observations reveals a requirement for \PIP{} at the base of cilia
  in regulating TZ length and function.
\end{abstract}

@@

In the Drosophila male germline, nascent TZs first assemble on basal bodies
during early G2 phase in spermatocytes and anchor directly to the plasma membrane.
This is followed by establishment of cilium-membrane connections
through a poorly understood mechanism
involving microtubule rearrangements \citep{gottardo2013cilium} and a
ciliary membrane that persists through meiosis \citep{riparbelli2012assembly}.
Ciliogenesis begins with the assembly of TZ proteins at the tips of
the nascent basal body.
This is followed by the anchoring of the TZ to the membrane and
establishment of a compartmentalized space bounded by the ciliary membrane
and the TZ.
TZ maturation has been described in
\textit{Paramecium} \citep{aubusson2015transition}
\textit{Caenorrhabditis elegans} \citep{serwas2017centrioles} and
\textit{Drosophila melanogaster} \citep{gottardo2013cilium}
and is most readily observed by an increase in TZ length from nascent to mature.
This are probably similar to the initial steps of TZ assembly and reorganization
in vertebrates.

@@

\section{Methods}
\subsection{Transgenic flies}
Drosophila stocks were cultured on cornmeal molasses agar medium at 25$^{\circ}$C
and 50\% humidity.
Stocks expressing $\beta$\textit{2tubulin}::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3})
and $\beta$\textit{2tub}::YFP-Sktl (chromosome \textit{2})
were described previously \citep{wei2008depletion, fabian2010phosphatidylinositol}.
$\beta$\textit{2tub}::mCherry-Sktl was made as in \citep{wei2008depletion},
and a \textit{P}-element insertion on chromosome \textit{2} was used for rescue using the low-level
expression vector \textit{tv3} \citep{wong2005pip2}.
Ana1-tdTomato (chromosome \textit{2}) and Cep290-GFP (chromosome \textit{3}) were provided
by T. Avidor-Reiss \citep{basiri2014migrating}.
\textit{Sp}/\textit{CyO}; Unc-GFP was originally provided by M. Kernan \citep{baker2004mechanosensory}.
Stocks expressing GFP-tagged Chibby, B9d1, B9d2, Cc2d2a and Mks1 were generously
provided by B. Durand \citep{enjolras2012drosophila, vieillard2016transition}.
The \textit{onr} mutant was described previously \citep{giansanti2015exocyst}.
Stocks for generating \textit{sktl}\textsuperscript{2.3} clones were originally provided by
A. Guichet \citep{gervais2008pip5k}.
\textit{w}\textsuperscript{1118} was used as the wild-type control.

@@

\subsection{Fluorescence microscopy}
For live imaging, testes were dissected in phosphate bufferd saline (PBS).
If staining for chromatin, intact testes were incubated in PBS with
Hoechst (1:5000) for 5 minutes at this point.
Testes were transferred to a polylysine-coated glass slide in a drop of PBS,
ruptured using a syringe needle and
squashed under a glass coverslip using Kimwipes.
The edges of the coverslip were sealed with nail polish
and the specimen was visualized immediately using a fluorescence microscope.

For Taxol treatments, testes from larvae or pupae expressing
Ana1-tdTomato; Cep290-GFP were
dissected into Shields and Sang M3 medium (Sigma-Aldrich) supplemented
with a predefined
concentration of Taxol and incubated overnight in a humidified sterile
chamber in the dark at room temperature. They were then squashed
in PBS and visualized immediately.

@@

\subsection{Statistical methods}
Statistical analysis and graphing was performed using R.
A Gaussian jitter was applied when plotting
results in Figures 1 and 2 for clearer visualization of trends,
but raw data was used for all analysis.
Statistical tests for ``absence of phenotype'' were computed under a
hypothesis assuming binomial likelihood (i.e. assuming a fixed probability of the
phenotype occurring).
All $t$-tests were unpaired and two-sided.
A significance level of 0.01 was fixed \textit{a priori} for all classical analysis.
All raw data and code for analysis and plotting can be found online
at \url{http://www.github.com/alindgupta/germline-paper/}.

>>>>

%% \usepackage{xcolor}
%% \pagecolor[RGB]{42,47,56}
%% \color[RGB]{189,189,161}

@@

\begin{abstract}
  \vspace*{-0.7em}
  Cilia are sensory organelles that are important for human development
  and physiology.
  A large number of genetic disorders affecting cilia are associated with
  mutations in proteins that localize to the transition zone (TZ),
  a structure at the base of cilia required for ciliogenesis and
  regulation of trafficking in and out of the cilium.
  Here, we report that the membrane lipid phosphatidylinositol
  4,5-bisphosphate(\PIP{}) is essential for proper maturation and function
  of TZs in the male \textit{Drosophila melanogaster} germline.
  Reduction of cellular \PIP{} levels by expression of the
  \textit{Salmonella} phosphoinositide phosphatase SigD or mutation of
  the type I phosphatidylinositol phosphate kinase (PIPKI) Skittles (Sktl)
  induces hyperelongation of TZs following their docking at the plasma
  membrane.
  We provide evidence that these hyperelongated TZs are functionally
  defective, and that the Exo84 mutant \textit{onion rings}
  \textit{onr} decouples TZ hyperelongation from the role for
  \PIP{} in cilium-membrane tethering.
  Our observations reveals a requirement for \PIP{} at the base of cilia
  in regulating TZ length and function.
\end{abstract}

@@

In the Drosophila male germline, nascent TZs first assemble on basal bodies
during G2 phase in spermatocytes and anchor to the plasma membrane.
This is followed by establishment of cilium-membrane connections
through a poorly understood mechanism
involving microtubule rearrangements \citep{gottardo2013cilium} and a
ciliary membrane that persists through meiosis \citep{riparbelli2012assembly}.
Ciliogenesis begins with the assembly of TZ proteins at the tips of
the nascent basal body.
This is followed by the anchoring of the TZ to the membrane and
establishment of a compartmentalized space bounded by the ciliary membrane
and the TZ.
TZ maturation has been described in
\textit{Paramecium} \citep{aubusson2015transition}
\textit{Caenorrhabditis elegans} \citep{serwas2017centrioles} and
\textit{Drosophila melanogaster} \citep{gottardo2013cilium}
and is most readily observed by an increase in TZ length from nascent to mature.
This are probably similar to the initial steps of TZ assembly and reorganization
in vertebrates.

@@

\section{Methods}
\subsection{Transgenic flies}
Drosophila stocks were cultured on cornmeal molasses agar medium at 25$^{\circ}$C
and 50\% humidity.
Stocks expressing $\beta$\textit{2t}::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3})
and $\beta$\textit{2t}::YFP-Sktl (chromosome \textit{2})
were described previously \citep{wei2008depletion, fabian2010phosphatidylinositol}.
$\beta$\textit{2t}::mCherry-Sktl was made as in \citep{wei2008depletion},
and a \textit{P}-element insertion on chromosome \textit{2} was used for rescue using the low-level
expression vector \textit{tv3} \citep{wong2005pip2}.
Ana1-tdTomato (chromosome \textit{2}) and Cep290-GFP (chromosome \textit{3}) were provided
by T. Avidor-Reiss \citep{basiri2014migrating}.
\textit{Sp}/\textit{CyO}; Unc-GFP was originally provided by M. Kernan \citep{baker2004mechanosensory}.
Stocks expressing GFP-tagged Chibby, B9d1, B9d2, Cc2d2a and Mks1 were
provided by B. Durand \citep{enjolras2012drosophila, vieillard2016transition}.
The \textit{onr} mutant was described previously \citep{giansanti2015exocyst}.
Stocks for generating \textit{sktl}\textsuperscript{2.3} clones were originally provided by
A. Guichet \citep{gervais2008pip5k}.
\textit{w}\textsuperscript{1118} was used as the wild-type control.

@@

\subsection{Fluorescence microscopy}
For live imaging, testes were dissected in phosphate bufferd saline (PBS).
If staining for chromatin, intact testes were incubated in PBS with
Hoechst (1:5000) for 5 minutes at this point.
Testes were transferred to a polylysine-coated glass slide in a drop of PBS,
ruptured using a syringe needle and
squashed under a glass coverslip using Kimwipes.
The edges of the coverslip were sealed with nail polish
and the specimen was visualized immediately using an epifluorescence microscope.

For Taxol treatments, testes from larvae or pupae expressing
Ana1-tdTomato; Cep290-GFP were
dissected into Shields and Sang M3 medium (Sigma-Aldrich) supplemented
with a predefined
concentration of Taxol and incubated overnight in a humidified sterile
chamber in the dark at room temperature. They were then squashed
in PBS and imaged live.

@@

\subsection{Statistical methods}
Statistical analysis and graphing was performed using R (version 3.4)
\citep{r}.
A Gaussian jitter was applied when plotting
results in Figures 1 and 2 for clearer visualization of trends,
but raw data was used for all analysis.
Statistical tests for ``absence of phenotype'' were computed under a
hypothesis assuming binomial likelihood (i.e. assuming a fixed probability of the
phenotype occurring).
All $t$-tests were unpaired and two-sided.
A significance level of 0.01 was fixed \textit{a priori} for all classical analysis.
All raw data and code for analysis and plotting can be found online
at \url{http://www.github.com/alindgupta/germline-paper/}.
